Parameters estimation via HOSVD

### 2025-01-03 Code/R/Research/HOSVD parameters estimate.Rmd
Multivariate rmse with hooi
Plots fixes

## Графики RMSE
```{r}
pltnms <- c("_no_rates", "_small_eq_rates", "_large_eq_rates", "")
pn <- 1

@@

rec.plot <- rec.df |> ggplot() +
  geom_line(aes(
    x = dims,
    y = RMSE,
    group = `trunc dims`,
    colour = `trunc dims`,
    linetype = `trunc dims`
  ), lwd = 1.2) + 
  geom_abline(slope = 0, intercept = min.ssa.rmse[1], col = "gray10", lty = 3) +
  annotate(geom = "text", x = 5, y = min.ssa.rmse[1] * 1.02, label = "SSA min RMSE") +
  ylim(min.ssa.rmse[1], 0.0245) + 
  theme(axis.text.x = element_text(angle = 90))

plot.save(
  rec.plot,
  paste0("./img/rec_dim_rmse", plot.name, ".pdf"),
  pdf,
  width = 9,
  height = 6,
  save = save
)
```

@@

min.ssa.rrmse <- lapply(
  list(
    rate1 = rate1.ssa.rrmse,
    rate2 = rate2.ssa.rrmse,
    freq1 = freq1.ssa.rrmse,
    freq2 = freq2.ssa.rrmse
  ),
  (\(v) c(min(v), which.min(Ls[v])))
)

@@

## Графики RRMSE
```{r}
pltnms <- c("_no_rates", "_small_eq_rates", "_large_eq_rates", "")
pn <- 1

load(file = paste0("./Research/comp_results/dim_rrmse", pltnms[pn], "_tens.RData"))
load(file = paste0("./Research/comp_results/dim_rrmse", pltnms[pn], "_ssa.RData"))
```

```{r}
rate1.df <- rate1.rrmse |> as.data.frame() |> 
   mutate(dims = factor(x = apply(tens.dims, 1, paste, collapse = "x"),
                       levels = apply(tens.dims, 1, paste, collapse = "x"))) |>
  pivot_longer(!dims, names_to = "estim dim", names_prefix = "V", values_to = "RRMSE")

rate1.plot <- rate1.df |> ggplot() +
  geom_line(aes(
    x = dims,
    y = RRMSE,
    group = `estim dim`,
    colour = `estim dim`,
    linetype = `estim dim`
  ), lwd = 1.2) + 
  geom_abline(slope = 0, intercept = min.ssa.rrmse$rate1[1], col = "gray10", lty = 3) + 
  annotate(geom = "text", x = 5, y = min.ssa.rrmse$rate1[1] * 1.05, label = "SSA min RRMSE") +
  theme(axis.text.x = element_text(angle = 90))

plot.save(
  rate1.plot,
  paste0("./img/rate1_dims", plot.name, ".pdf"),
  pdf,
  width = 9,
  height = 6,
  save = save
)
```

```{r}
rate2.df <- rate2.rrmse |> as.data.frame() |> 
   mutate(dims = factor(x = apply(tens.dims, 1, paste, collapse = "x"),
                       levels = apply(tens.dims, 1, paste, collapse = "x"))) |>
  pivot_longer(!dims, names_to = "estim dim", names_prefix = "V", values_to = "RRMSE")

rate2.plot <- rate2.df |> ggplot() +
  geom_line(aes(
    x = dims,
    y = RRMSE,
    group = `estim dim`,
    colour = `estim dim`,
    linetype = `estim dim`
  ), lwd = 1.2) + 
  geom_abline(slope = 0, intercept = min.ssa.rrmse$rate2[1], col = "gray10", lty = 3) + 
  annotate(geom = "text", x = 5, y = min.ssa.rrmse$rate2[1] * 1.05, label = "SSA min RRMSE") +
  theme(axis.text.x = element_text(angle = 90))

plot.save(
  rate2.plot,
  paste0("./img/rate2_dims", plot.name, ".pdf"),
  pdf,
  width = 9,
  height = 6,
  save = save
)
```

@@

freq1.plot <- freq1.df |> ggplot() +
  geom_line(aes(
    x = dims,
    y = RRMSE,
    group = `estim dim`,
    colour = `estim dim`,
    linetype = `estim dim`
  ), lwd = 1.2) + 
  geom_abline(slope = 0, intercept = min.ssa.rrmse$freq1[1], col = "gray10", lty = 3) + 
  annotate(geom = "text", x = 5, y = min.ssa.rrmse$freq1[1] * 1.05, label = "SSA min RRMSE") +
  theme(axis.text.x = element_text(angle = 90))

plot.save(
  freq1.plot,
  paste0("./img/freq1_dims", plot.name, ".pdf"),
  pdf,
  width = 9,
  height = 6,
  save = save
)
```

@@

freq2.plot <- freq2.df |> ggplot() +
  geom_line(aes(
    x = dims,
    y = RRMSE,
    group = `estim dim`,
    colour = `estim dim`,
    linetype = `estim dim`
  ), lwd = 1.2) + 
  geom_abline(slope = 0, intercept = min.ssa.rrmse$freq2[1], col = "gray10", lty = 3) + 
  annotate(geom = "text", x = 5, y = min.ssa.rrmse$freq2[1] * 1.05, label = "SSA min RRMSE") +
  theme(axis.text.x = element_text(angle = 90))

plot.save(
  freq2.plot,
  paste0("./img/freq2_dims", plot.name, ".pdf"),
  pdf,
  width = 9,
  height = 6,
  save = save
)
```

@@

```{r}
if (pltnms[pn] != "_no_rates")
{
  rate1.df <- rate1.mult.rrmse |> as.data.frame() |> mutate(L = Ls) |>
    pivot_longer(!L, names_to = "Method", values_to = "RRMSE")
  rate1.plot <- rate1.df |> ggplot() +
    geom_line(aes(
      x = L,
      y = RRMSE,
      colour = Method,
      linetype = Method
    ), lwd = 1.2)

@@

```{r}
if (pltnms[pn] != "_no_rates")
{
  rate2.df <- rate2.mult.rrmse |> as.data.frame() |> mutate(L = Ls) |>
    pivot_longer(!L, names_to = "Method", values_to = "RRMSE")
  rate2.plot <- rate2.df |> ggplot() + geom_line(aes(
    x = L,
    y = RRMSE,
    colour = Method,
    linetype = Method
  ), lwd = 1.2)

@@

```{r}
freq1.df <- freq1.mult.rrmse |> as.data.frame() |> mutate(L = Ls) |>
  pivot_longer(!L, names_to = "Method", values_to = "RRMSE")
freq1.plot <- freq1.df |> ggplot() + geom_line(aes(
  x = L,
  y = RRMSE,
  colour = Method,
  linetype = Method
), lwd = 1.2)

@@

```{r}
freq2.df <- freq2.mult.rrmse |> as.data.frame() |> mutate(L = Ls) |>
  pivot_longer(!L, names_to = "Method", values_to = "RRMSE")
freq2.plot <- freq2.df |> ggplot() + geom_line(aes(
  x = L,
  y = RRMSE,
  colour = Method,
  linetype = Method
), lwd = 1.2)

@@

    rec.tmssa <- tens_mssa_reconstruct(
      x,
      L = L,
      groups = groups,
      groups3 = groups3,
      status = FALSE
    )

>>>>

@@

rec.plot <- rec.df |> ggplot() +
  geom_line(aes(
    x = dims,
    y = RMSE,
    group = `trunc dims`,
    colour = `trunc dims`,
    linetype = `trunc dims`
  ), lwd = 1.2) + 
  geom_abline(
    slope = 0,
    intercept = min.ssa.rmse[1],
    col = "gray10",
    lty = 3
  ) +
  ylim(min.ssa.rmse[1] * 0.985, NA) +
  annotate(
    geom = "text",
    x = 5,
    y = min.ssa.rmse[1] * 0.99,
    label = paste0("SSA min RMSE, L=", min.ssa.rmse[2])
  ) +
  theme(axis.text.x = element_text(angle = 90))

plot.save(
  rec.plot,
  paste0("./img/rec_dim_rmse", pltnms[pn], ".pdf"),
  pdf,
  width = 9,
  height = 6,
  save = save
)
```

@@

@@

## Графики RRMSE
```{r}
pltnms <- c("_no_rates", "_small_eq_rates", "_large_eq_rates", "")
pn <- 4

load(file = paste0("./Research/comp_results/dim_rrmse", pltnms[pn], "_tens.RData"))
load(file = paste0("./Research/comp_results/dim_rrmse", pltnms[pn], "_ssa.RData"))

min.ssa.rrmse <- lapply(
  list(
    rate1 = rate1.ssa.rrmse,
    rate2 = rate2.ssa.rrmse,
    freq1 = freq1.ssa.rrmse,
    freq2 = freq2.ssa.rrmse
  ),
  (\(v) c(min(v), Ls[which.min(v)]))
)
```

```{r}
if (pltnms[pn] != "_no_rates")
{
  rate1.df <- rate1.rrmse |> as.data.frame() |>
    mutate(dims = factor(
      x = apply(tens.dims, 1, paste, collapse = "x"),
      levels = apply(tens.dims, 1, paste, collapse = "x")
    )) |>
    pivot_longer(
      !dims,
      names_to = "estim dim",
      names_prefix = "V",
      values_to = "RRMSE"
    )

  rate1.plot <- rate1.df |> ggplot() +
    geom_line(
      aes(
        x = dims,
        y = RRMSE,
        group = `estim dim`,
        colour = `estim dim`,
        linetype = `estim dim`
      ),
      lwd = 1.2
    ) +
    geom_abline(
      slope = 0,
      intercept = min.ssa.rrmse$rate1[1],
      col = "gray10",
      lty = 3
    ) +
    annotate(
      geom = "text",
      x = 7,
      y = min.ssa.rrmse$rate1[1] * 0.95,
      label =  paste0("ESPRIT min RRMSE, L=", min.ssa.rrmse$rate1[2])
    ) +
    theme(axis.text.x = element_text(angle = 90))

  plot.save(
    rate1.plot,
    paste0("./img/rate1_dims", pltnms[pn], ".pdf"),
    pdf,
    width = 9,
    height = 6,
    save = save
  )
}
```

```{r}
if (pltnms[pn] != "_no_rates")
{
  rate2.df <- rate2.rrmse |> as.data.frame() |>
    mutate(dims = factor(
      x = apply(tens.dims, 1, paste, collapse = "x"),
      levels = apply(tens.dims, 1, paste, collapse = "x")
    )) |>
    pivot_longer(
      !dims,
      names_to = "estim dim",
      names_prefix = "V",
      values_to = "RRMSE"
    )

  rate2.plot <- rate2.df |> ggplot() +
    geom_line(
      aes(
        x = dims,
        y = RRMSE,
        group = `estim dim`,
        colour = `estim dim`,
        linetype = `estim dim`
      ),
      lwd = 1.2
    ) +
    geom_abline(
      slope = 0,
      intercept = min.ssa.rrmse$rate2[1],
      col = "gray10",
      lty = 3
    ) +
    annotate(
      geom = "text",
      x = 7,
      y = min.ssa.rrmse$rate2[1] * 0.95,
      label =  paste0("ESPRIT min RRMSE, L=", min.ssa.rrmse$rate2[2])
    ) +
    theme(axis.text.x = element_text(angle = 90))

  plot.save(
    rate2.plot,
    paste0("./img/rate2_dims", pltnms[pn], ".pdf"),
    pdf,
    width = 9,
    height = 6,
    save = save
  )
}
```

@@

freq1.plot <- freq1.df |> ggplot() +
  geom_line(aes(
    x = dims,
    y = RRMSE,
    group = `estim dim`,
    colour = `estim dim`,
    linetype = `estim dim`
  ), lwd = 1.2) + 
  geom_abline(
    slope = 0,
    intercept = min.ssa.rrmse$freq1[1],
    col = "gray10",
    lty = 3
  ) +
  annotate(
    geom = "text",
    x = 7,
    y = min.ssa.rrmse$freq1[1] * 0.95,
    label = paste0("ESPRIT min RRMSE, L=", min.ssa.rrmse$freq1[2])
  ) +
  theme(axis.text.x = element_text(angle = 90))

plot.save(
  freq1.plot,
  paste0("./img/freq1_dims", pltnms[pn], ".pdf"),
  pdf,
  width = 9,
  height = 6,
  save = save
)
```

@@

freq2.plot <- freq2.df |> ggplot() +
  geom_line(aes(
    x = dims,
    y = RRMSE,
    group = `estim dim`,
    colour = `estim dim`,
    linetype = `estim dim`
  ), lwd = 1.2) + 
  geom_abline(
    slope = 0,
    intercept = min.ssa.rrmse$freq2[1],
    col = "gray10",
    lty = 3
  ) +
  annotate(
    geom = "text",
    x = 7,
    y = min.ssa.rrmse$freq2[1] * 0.95,
    label = paste0("ESPRIT min RRMSE, L=", min.ssa.rrmse$freq2[2])
  ) +
  theme(axis.text.x = element_text(angle = 90))

plot.save(
  freq2.plot,
  paste0("./img/freq2_dims", pltnms[pn], ".pdf"),
  pdf,
  width = 9,
  height = 6,
  save = save
)
```

@@

```{r}
if (pltnms[pn] != "_no_rates")
{
  rate1.df <- rate1.mult.rrmse |> as.data.frame() |> mutate(L = Ls) |>
    pivot_longer(!L, names_to = "Method", values_to = "RRMSE") |>
    mutate(Method = ifelse(Method == "HO.MSSA", "HO-ESPRIT", "ESPRIT"))
  rate1.plot <- rate1.df |> ggplot() +
    geom_line(aes(
      x = L,
      y = RRMSE,
      colour = Method,
      linetype = Method
    ), lwd = 1.2)

@@

```{r}
if (pltnms[pn] != "_no_rates")
{
  rate2.df <- rate2.mult.rrmse |> as.data.frame() |> mutate(L = Ls) |>
    pivot_longer(!L, names_to = "Method", values_to = "RRMSE") |>
    mutate(Method = ifelse(Method == "HO.MSSA", "HO-ESPRIT", "ESPRIT"))
  rate2.plot <- rate2.df |> ggplot() + geom_line(aes(
    x = L,
    y = RRMSE,
    colour = Method,
    linetype = Method
  ), lwd = 1.2)

@@

```{r}
freq1.df <- freq1.mult.rrmse |> as.data.frame() |> mutate(L = Ls) |>
  pivot_longer(!L, names_to = "Method", values_to = "RRMSE") |>
    mutate(Method = ifelse(Method == "HO.MSSA", "HO-ESPRIT", "ESPRIT"))
freq1.plot <- freq1.df |> ggplot() + geom_line(aes(
  x = L,
  y = RRMSE,
  colour = Method,
  linetype = Method
), lwd = 1.2)

@@

```{r}
freq2.df <- freq2.mult.rrmse |> as.data.frame() |> mutate(L = Ls) |>
  pivot_longer(!L, names_to = "Method", values_to = "RRMSE") |>
    mutate(Method = ifelse(Method == "HO.MSSA", "HO-ESPRIT", "ESPRIT"))
freq2.plot <- freq2.df |> ggplot() + geom_line(aes(
  x = L,
  y = RRMSE,
  colour = Method,
  linetype = Method
), lwd = 1.2)

@@

    rec.tmssa <- tens_mssa_reconstruct(
      x,
      L = L,
      groups = groups,
      groups3 = groups3,
      decomp = "HOOI",
      status = FALSE
    )
